Sampling in Decisions from Experience

### 2021-10-11 slides_modelers-meeting.Rmd
Final version

## Prospects and Sampling

- Standard paradigm: Choice between 2 or multiple prospects

- *Prospects*: Probability spaces $(\Omega, \mathcal{F}, P)$, where 
$$
\Omega = \{\omega_1, ..., \omega_n\}
$$
and 
$$
P = \{p(\omega_1), ..., p(\omega_n)\}
$$

- *Single sample*: Realization of a random variable:
$$
X(\omega \in \Omega) = x 
$$

- *Sequential sampling*: Generating a sequence of single samples in discrete time: 
$$
X_i = X_1, ..., X_n 
$$

@@

- Decisions from Description (DfD): Function of symbolical descriptions of prospects:  
$$
D:= f((\Omega_1, \mathcal{F}_1, P_1), ..., (\Omega_k, \mathcal{F}_k, P_k))
$$

@@

- Consider two prospects $(\Omega_X, \mathcal{F}_X, P_X)$ and $(\Omega_Y, \mathcal{F}_Y, P_Y)$ and the ground model for DfE
$$
D := f(X_i, Y_i) 
$$

@@

## Predicting Choices from the Stochastic Model

- $n$ and $p$ of the binomial distribution are influenced by the sampling and decision strategies:

### Comprehensive Sampling and Summary Decisions

- $n = 1$  
- $p$: For $\lim_{N_X, N_Y  \to \infty}$, $p (\overline{X} - \overline{Y}> 0) \approx p (E(X) - E(Y))$ 
- Choices should become *"normative"*, i.e., linear weighting and value function

### Piecewise Sampling and Round-wise Decisions

- $n \geq 1$ and $N_X, N_Y = 1$
- $p$: For $N_X, N_Y = 1$, $p (\overline{X} - \overline{Y} > 0) = p(\omega \in \Omega_X > \omega \in \Omega_Y)$
- Choices depend on probabilities in the mid-range, i.e., S-shaped weighting function and concave value function

>>>>

@@

- Decisions from Description (DfD): Function of symbolical descriptions of prospects (gambles):  
$$
D:= f((\Omega_1, P_1), ..., (\Omega_k, P_k))
$$

@@

@@
